Stats

### 2023-06-05 paper/manuscript.Rmd
add lifespan data

```{r setup, include = FALSE}
library("papaja")
library("ggplot2")
library("ggpubr")
library("tidyverse")
library("brms")
theme_set(theme_classic())
```

@@

```{r load_data}
# TODO: only hedge version

testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>%
  mutate_if(is.character, as.factor) %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")),
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "teens", "adults")),
    studytype = factor(studytype, levels = c("vali", "reli")),

    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
    # the smaller the value, the more central the position
    symmetricPosition = case_when(
                                  targetPosition == "5" | targetPosition == "6" ~ 1,
                                  targetPosition == "4" | targetPosition == "7" ~ 2,
                                  targetPosition == "3" | targetPosition == "8" ~ 3,
                                  targetPosition == "2" | targetPosition == "9" ~ 4,
                                  targetPosition == "1" | targetPosition == "10" ~ 5,
                       ),

    # distance between target and click in balloon widths (balloon width is 160 SVG units)
    clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
  )
```

@@

```{r dev_sample}
dev_kids <- testtrials %>%
  filter(studytype == "vali" & age < 18) %>%
  group_by(datacollection, agegroup) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>%
  summarise(
    nTotal = n_distinct(subjID),
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )

dev_adults <- testtrials %>%
  filter(studytype == "vali" & sample == "adults") %>%
  ungroup() %>%
  mutate(
    gender = ifelse(is.na(gender), 0, paste(gender)),
    female = ifelse(gender == "f", 1, 0),
  ) %>%
  summarise(
    nTotal = n_distinct(subjID),
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )
```

@@

We collected data from an in-person child sample, a remote child an teenager sample, and a remote adult sample. In-person testing with children took place in kindergartens in Leipzig, Germany.

The in-person child sample consisted of `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised"])` children, including `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` 3-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` 4-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` girls), and `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` 5-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` girls).

For the remote child and teenager sample, we recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.

The remote child and teenager sample consisted of `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised"])` children, including `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` 3-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` 4-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` 5-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` 6-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` 7-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` 8-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` 9-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` 10-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` 11-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` 12-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` 13-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` 14-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` 15-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` 16-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` girls), and `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` 17-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` girls).

@@

Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool. Participants consisted of `r dev_adults$nTotal` English-speakers with an average age of `r dev_adults$meanAge` years (SD = `r dev_adults$sdAge`, range = `r dev_adults$minAge` - `r dev_adults$maxAge`, `r dev_adults$nFemales` females).

>>>>

```{r setup, include = FALSE}
library("tidyverse")
library("papaja")
theme_set(theme_classic())
```

@@

```{r load_data}
tango_lifespan <- readRDS("../data/tango-lifespan.rds")
tango_model <- readRDS("../data/tango-model.rds")
magnet <- readRDS("../data/magnet-data.rds")
```

@@

```{r dev_sample}
lifespan_sample <- tango_lifespan %>% 
  group_by(age_group) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    n_total = n_distinct(subj_id), 
    age_mean = mean(age, na.rm = T) %>% round(2),
    age_sd = sd(age, na.rm = T) %>% round(2),
    age_min = min(age, na.rm = T),
    age_max = max(age, na.rm = T),
    n_females = ceiling(sum(female/15)),
  )
```

@@

We collected data from a remote child, teenager and adult sample.
For the remote child and teenager sample, we recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.

The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "3"])` 3-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "3"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "3"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "3"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "3"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "3"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "4"])` 4-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "4"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "4"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "4"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "4"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "4"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "5"])` 5-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "5"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "5"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "5"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "5"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "5"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "6"])` 6-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "6"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "6"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "6"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "6"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "6"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "7"])` 7-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "7"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "7"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "7"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "7"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "7"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "8"])` 8-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "8"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "8"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "8"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "8"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "8"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "9"])` 9-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "9"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "9"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "9"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "9"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "9"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "10"])` 10-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "10"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "10"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "10"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "10"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "10"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "11"])` 11-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "11"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "11"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "11"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "11"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "11"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "12"])` 12-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "12"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "12"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "12"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "12"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "12"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "13"])` 13-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "13"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "13"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "13"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "13"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "13"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "14"])` 14-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "14"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "14"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "14"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "14"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "14"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "15"])` 15-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "15"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "15"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "15"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "15"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "15"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "16"])` 16-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "16"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "16"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "16"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "16"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "16"])` girls), and `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "17"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "17"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "17"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "17"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "17"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "17"])` girls).

@@

<!-- Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool. Participants consisted of `r lifespan_sample$n_total` English-speakers with an average age of `r lifespan_sample$age_mean` years (SD = `r lifespan_sample$age_sd`, range = `r lifespan_sample$age_min` - `r lifespan_sample$age_max`, `r lifespan_sample$n_females` females). -->

### 2023-06-05 stats/analysis.Rmd
add lifespan data

options(scipen = 999)
theme_set(theme_classic())
# Seed for random number generation
set.seed(42)
```

```{r load_data}
# testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
#   # determine order of factors
#   mutate(
#     targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
#     studyversion = factor(studyversion, levels = c("hedge", "box")), 
#     datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
#     sample = factor(sample, levels = c("kids", "adults")), 
#     studytype = factor(studytype, levels = c("vali", "vali2", "reli")),
#     
#     # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
#     # the smaller the value, the more central the position
#     symmetricPosition = ifelse(studyversion == "box", 
#                                # for box version
#                                case_when(
#                                   targetPosition == "box3" ~ 0, 
#                                   targetPosition == "box2" | targetPosition == "box4" ~ 1,
#                                   targetPosition == "box1" | targetPosition == "box5" ~ 2), 
#                                # for hedge version
#                                targetCentralityX
#                        ), 
#     
#     # distance between target and click in balloon widths (balloon width is 160 SVG units)
#     clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
#   )
```

>>>>

options(scipen = 999)
theme_set(theme_classic())

# Seed for random number generation
set.seed(42)
```

```{r load_data}
tango_lifespan <- readRDS("../data/tango-lifespan.rds")
tango_model <- readRDS("../data/tango-model.rds")
magnet <- readRDS("../data/magnet-data.rds")
```

# DEVELOPMENTAL TRAJECTORY
```{r lifespan_sample}
lifespan_sample <- tango_lifespan %>% 
  group_by(age_group) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    n_total = n_distinct(subj_id), 
    age_mean = mean(age, na.rm = T) %>% round(2),
    age_sd = sd(age, na.rm = T) %>% round(2),
    age_min = min(age, na.rm = T),
    age_max = max(age, na.rm = T),
    n_females = ceiling(sum(female/15)),
  )
```

```{r variation_preparateData}
lifespan_variation <- tango_lifespan %>% 
  group_by(subj_id, age, age_group) %>%
  summarise(mean = mean(click_dist_balloons, na.rm = TRUE))
```

```{r lifespan_plot}
ggplot(data = lifespan_variation, aes(x = age, y = mean)) +
  geom_point(color = "darkgrey", alpha = 0.5) +
  geom_smooth(method = "loess", size = 1, se = F, color = "#006c66") + 
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target widths")

ggsave("../figures/tango_lifespan.png", width = 8, height = 4, scale = 1.2)
```

```{r lifespan_model}
mDataLifespan <- tango_lifespan %>% 
  mutate(
    symmetric_position = scale(symmetric_position),
    trial_nr = trial_nr - min(trial_nr), 
    click_dist = abs(click_dist_from_target_center_x),
  ) %>% 
  select(subj_id, age, age_centered, symmetric_position, trial_nr, click_dist, click_dist_balloons)

mLifespanNull <- brm(click_dist_balloons ~ age_centered + symmetric_position + trial_nr + (1 + symmetric_position + trial_nr | subj_id),
                    data = mDataLifespan,
                    family = lognormal(),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 4)

write.csv(mAgeHedge, "../saves/mLifespan.csv", quote = F, row.names = F)
saveRDS(mAgeHedge, "../saves/mLifespan.rds")
```

# COGNITIVE MODEL

```{r gazefunnel}
target_position_impr <- tango_model %>% 
  group_by(age_group, target_position) %>% 
  tidyboot_mean(column = click_dist_balloons, na.rm = TRUE)

target_position_impr_ind <- tango_model %>% 
  group_by(subj_id, age_group, target_position) %>% 
  tidyboot_mean(column = click_dist_balloons, na.rm = TRUE)

ggplot() +
  geom_point(data = target_position_impr_ind, aes(x = target_position, y = mean, col = as.factor(age_group)), alpha = .1, position = position_dodge(width = 0.3)) +

  geom_pointrange(data = target_position_impr, aes(x = target_position, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(age_group)), pch = 18,  size = 1, position = position_dodge(width = .3)) +

  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) + 
  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d"), breaks = c("3", "4", "5"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
    labs(x = "Target position (binned)", y = "Average imprecision in target widths", col = "Age in years")

ggsave("../figures/tango_gazefunnel.png", width = 6, height = 4, scale = 1.2)
```
